cvx-flats

### 2020-05-05 neurips-20/cvx-flats-statements.tex
Fixing consistency with respect to a property I hope

\subsection{Consistency \jessie{and calibration?} for convex losses}\label{subsec:convex-surrogates}

\begin{definition}[Consistent: loss]
	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
	we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{align*}
\end{definition}

@@

\begin{definition}[Consistent: property]
	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$ and $p_x$ is the conditional distribution on $Y$ given $X = x$,  we observe
	\begin{equation}
	\E_{(X,Y) \sim D} L(\Gamma(p_X), Y) \to \inf_{u \in \reals^d} \E_{Y \sim p_x} L(u, Y) \implies d(\E_X \Gamma(p_X), \Gamma(p_x)) \to 0 
	\end{equation}
	for all $x \in \X$.
%	equipped with the metric $d$ if, for all distributions $D$ over $\X \times \Y$, we have $d(f(X), \Gamma(P[Y|X])) < \epsilon \implies \E_{(X,Y) \sim D} \arginf_{f} L(f(X), Y).$
\end{definition}

@@

\begin{definition}[Convex Calibration Dimension]
The \emph{convex calibration dimension} $\ccdim(\ell)$ of a loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
\end{definition}

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss $L$ is consistent with respect to a property $\Gamma$, then it is calibrated with respect to $\Gamma$.
	\jessie{Probably appendix later.}
\end{proposition}
\begin{proof}
	\jessie{...}
\end{proof}

@@

\begin{definition}[Subspace of feasible directions]
	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
\end{definition}

@@

\begin{proposition}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $(L, \psi)$ is also consistent with respect to $\ell$, and therefore $L$ indirectly elicits $\gamma$.
\end{proof}

>>>>

\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}

\begin{definition}[Consistent: loss]
	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
	we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}

@@

\begin{definition}[Consistent: property]
	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
	\begin{equation}
	d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
	\end{equation}
	where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
%	equipped with the metric $d$ if, for all distributions $D$ over $\X \times \Y$, we have $d(f(X), \Gamma(P[Y|X])) < \epsilon \implies \E_{(X,Y) \sim D} \arginf_{f} L(f(X), Y).$
\end{definition}

@@

\begin{definition}[Convex Calibration Dimension]
The \emph{convex calibration dimension} $\ccdim(\ell)$ of a discrete loss $\ell$ is the minimum dimension $d$ such that there is a convex loss $L: \reals^d \times \Y \to \reals$ and link $\psi$ such that $L$ is calibrated with respect to $\ell$.
\end{definition}

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a property $\gamma$, then they are calibrated with respect to $\gamma$.
	\jessie{Probably appendix later.}
\end{proposition}
\begin{proof}
	\jessie{...}
\end{proof}

@@

\begin{definition}[Subspace of feasible directions]
	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C$ and $p - \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$ .
\end{definition}

@@

\begin{proposition}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$.
\end{proof}
